NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2017-01-10 ms_nihao_budget.tex
make clean files

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. 
{\bf It suggests that the baryon fraction correlates 
strongly with halo mass, due to the deeper potential well of the halo and/or stronger 
ram pressure experienced by the outflowing gas. However, Fig.~\ref{fig:fire_com}
 suggests that the 
 specific implementation of the feedback model does not matter, as long as the feedback 
is efficient in driving outflows.}

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the {\bf fiducial
baryonic mass defined by Eq.~\ref{equ:mb}}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes.  It is a
  radius within the high-resolution volume of the simulations since
  the {\bf mass fraction of low resolution dark matter particles}
  in a shell between 0.9 and  1.0 $\Rbar$
  shows most NIHAO galaxies have a fraction close to 0, with largest
  only around 10 - 20\%.  Fig.~\ref{fig:missvr} shows the baryon
radius of each galaxy as function of the virial mass. In physical
units, we find that the baryon radius generally increases with virial
mass. When normalized by the virial radius, the distance baryons are
ejected gradually decreases as halo mass increases, varying from
$\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$ to
$\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

{\bf Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
  and warm-hot gas color coded by the number of dark matter particles
  inside the virial radius. Since one can imagine that with increased
  resolution, higher densities can be achieved in the CGM, potential
  leading to more cooling and larger cold/cool gas fractions.  In our
  simulations we find no dependence of stars and gas fractions with particle
  number, indicating these quantities are not sensitive to numerical
  resolution using the NIHAO sub-grid model.}

>>>>

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. 
It suggests that the baryon fraction correlates 
strongly with halo mass, due to the deeper potential well of the halo and/or stronger 
ram pressure experienced by the outflowing gas. However, Fig.~\ref{fig:fire_com}
 suggests that the 
 specific implementation of the feedback model does not matter, as long as the feedback 
is efficient in driving outflows.

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes.  It is a
  radius within the high-resolution volume of the simulations since
  the mass fraction of low resolution dark matter particles
  in a shell between 0.9 and  1.0 $\Rbar$
  shows most NIHAO galaxies have a fraction close to 0, with largest
  only around 10 - 20\%.  Fig.~\ref{fig:missvr} shows the baryon
radius of each galaxy as function of the virial mass. In physical
units, we find that the baryon radius generally increases with virial
mass. When normalized by the virial radius, the distance baryons are
ejected gradually decreases as halo mass increases, varying from
$\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$ to
$\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

 Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
  and warm-hot gas color coded by the number of dark matter particles
  inside the virial radius. Since one can imagine that with increased
  resolution, higher densities can be achieved in the CGM, potential
  leading to more cooling and larger cold/cool gas fractions.  In our
  simulations we find no dependence of stars and gas fractions with particle
  number, indicating these quantities are not sensitive to numerical
  resolution using the NIHAO sub-grid model.
